Screen Time Review of Reviews Summary

### 2021-08-16 index.Rmd
Add reverse coding
Fix Ns with mean imputation

After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total effect size. This process yielded `r prisma$data$value[9]` unique effects/outcome combinations.

@@

Currently, individual data has been extracted and cleaned for `r nrow(studies_results)` effect sizes.

@@

>>>>

After extracting data, we examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total effect size. This process yielded `r nrow(effects_clean)` unique effects/outcome combinations contributed from `r prisma$data$value[9]` papers.

@@

Currently, individual data has been extracted and cleaned for `r nrow(studies_results)` effect sizes, out of `r nrow(effects_clean)` total effects (`r scales::percent(nrow(studies_results)/nrow(effects_clean))`) .

@@

The following warnings were noted during the project build:

```{r}
tar_meta(fields = warnings) %>% filter(!is.na(warnings)) %>% arrange(name)
```
